---
title: "Exam Two"
author: "Herrington"
date: "6/26/2020"
output: pdf_document
---

#Loading the dataset into a dataframe

#*Repo Link*
[Repo Link](https://github.com/Dawson-Herrington-98/datascienceclass)

#1 and 2
```{r}
library(rio)
library(dplyr)
library(doBy)
library(devtools)
library(remotes)
library(remote)
library(WDI)
library(data.table)
library(countrycode)
library(tidyverse)

inequality_data <- import("inequality.xlsx")
attach(inequality_data)
```

#3
The data is cross sectional, it is all from 2015.
What follows are pulled years, all 2015
```{r}
print(year)
```

#4
Gini scores for Sweden and Denmark
```{r}
ginisub <- subset(inequality_data, select = c("inequality_gini"))
sweGini <-filter(ginisub,country=="Sweden")
denmGini <-filter(ginisub,country=="Denmark")
#printing

print(paste("Sweden:",sweGini,"and Denmark:",denmGini))
```

#5
Brazil Inequality Gini Score
```{r}
brazGini <- filter(ginisub,country=="Brazil")
print(paste("Brazil:",brazGini))
```

#6
It seems to be better to have a generally lower gini score

#7
```{r}
head(inequality_data)
```

#8
```{r}

accent.remove <- function(n)
{
  inequality_data$country[inequality_data$country=="Belarús"] = "Belarus"
}
accent.remove()


```


#9
sort
```{r}
inequality_data = inequality_data[order(inequality_data$inequality_gini),]
head(inequality_data)
```

#10
Mean gini score
```{r}
mean(inequality_gini,na.rm = TRUE)
```
The mean iniequality gini score is 36.81375

#11
```{r}
ifelse(test = inequality_data$inequality_gini > mean(inequality_gini,na.rm = TRUE),
       yes = high_inequality <- 0, no = low_inequality <- 1)
```

#12
Cross Tabulation
```{r}
#summaryBy(high_inequality ~ low_inequality, data=inequality_data, FUN=c(mean,length))
```

#13
```{r}
orgs <- c('World Bank', 'African Development Bank', 'Bill and Melinda Gates Foundation')
for (i in orgs){
  print(i)
}
```

#14
I picked income share held by the lowest 20%. I feel that this is a good indicator
because the lower that income share is the higher inequality would likely be as
wealth would be accumulating above that 20%.

#15
```{r}
WDI_D = WDI(country = "all",
indicator = c("SI.DST.FRST.20"), start = 2015, end = 2015, extra = FALSE, cache = NULL)
```

#16
Rename the variable
```{r}
setnames(WDI_D,"SI.DST.FRST.20", "Income Share Lowest 20%")
```

#17
```{r}
#assign country codes and filter
WDI_D$country_code = countrycode(sourcevar = WDI_D$iso2c,
origin = "iso2c", destination = "iso3c", warn = TRUE)
WDI_D <- WDI_D %>% dplyr::filter(!(country_code=="NA"))

WDI_D <-
WDI_D %>% dplyr::filter(!(country_code=="NA"))

#merging
#merged_df = left_join(x=inequality_data, y=WDI_D, by =c("country_code", "year"))
```

#18
```{r}

```

#23 Stata data set
I did not make it here as I encountered some issues. I am still doing this part to
prove that I understand how to export
```{r}
export(inequality_data, file = "clean_dataset.dta")
```












